Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
intro

Another strength of hypercoercion over coercion is that hypercoercion might 
have a more compact memory representations ...
\todo[inline]{Could Jeremy explain here why hypercoercion is more compact in 
memory? -KC}

Many of the existing research on coercions or threesomes include proof(s) of 
correctness, that is, the cast calculus reduces to an observation ($ e 
\Downarrow o $) if and only if their calcului reduce to the same observation ($ 
e \Downarrow_{*} o $), where an observation is either a value constructor or 
blame. 
Despite the striking similarity of these proofs, they are all built from ground 
up.

@@

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. 
\todo[inline]{Why do we need to explain why both LD and LUD? -KC
  \\---\\
Because the paper includes both. -JS}

Here are our major contribution:
\begin{itemize}
	\item hypercoercion, a new space-efficient cast representation, which has a 
	structurally recursive composition and has a more compact memory 
	representation.
	\item a framework in Agda for proving correctness of cast represantations. 
	We conjecture that both coercion and threesome can fit into this framework.
	\item a formal proof that hypercoercion respect the semantics of cast 
	calculus
\end{itemize}

>>>>

Another strength of hypercoercion over coercion is that hypercoercion might 
have a more compact memory representations. In Grift 
\citep{kuhlenschmidt2018efficient}, the longest coercions are represented with
two cons boxes. But for hypercoercion, we are optimistic that one cons box 
suffices. Using less cons boxes saves memory as well as running time.
\todo[inline]{
	Could Jeremy help explain explaining why hypercoercion is more compact in 
	memory?
	Cons boxes seem to be non-standard, but I don't know a better name.
 -KC}

Many of the existing research on coercions or threesomes include proof(s) of 
correctness, that is, the cast calculus reduces to an observation ($ e 
\Downarrow o $) if and only if their space-efficient calcului reduce to the 
same observation ($ e \Downarrow_{*} o $), where an observation is either a 
value constructor or 
blame. 
Despite the striking similarity of these proofs, they are all built from ground 
up.

@@

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. We are unaware of any 
strong argument favoring D or UD, so we study both \lazyD\ and \lazyUD.
\todo[inline]{Why do we need to explain why both LD and LUD? -KC
  \\---\\
Because the paper includes both. -JS
\\---\\
Fixed. -KC}

Here are our major contribution:
\begin{itemize}
	\item hypercoercion, a new space-efficient cast representation, which has a 
	structurally recursive composition and a more compact memory 	
	representation.
	\item a framework in Agda for proving correctness of cast represantations. 
	We conjecture that both coercion and threesome can fit into this framework.
	\item a formal proof that hypercoercion respects the semantics of cast 
	calculus
\end{itemize}
